*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-23 Code/Manuscript_O2.Rmd
removed green data from 1 line in results section. knit to .docx

XXXXXCHECK WHEN MIREILLE ADDS Colour specific fitsXXX This inhibition initially suggested that blue wavebands triggered photoinhibition at significantly lower levels of Photosynthetically Active Radiation (PAR) compared to other spectral wavebands. However, considering the equivalent cumulative diel absorbed PUR of the blue waveband, all treatments including blue, white LED, red and green waveband exhibited approximately the same growth saturation. XXXX

>>>>

XXXXXCHECK WHEN MIREILLE ADDS Colour specific fitsXXX This inhibition initially suggested that blue wavebands triggered photoinhibition at significantly lower levels of Photosynthetically Active Radiation (PAR) compared to other spectral wavebands. However, considering the equivalent cumulative diel absorbed PUR of the blue waveband, all treatments including white LED, red, and blue waveband exhibited approximately the same growth saturation. XXXX
